Artin Group Presentations Arising from Cluster Algebras

### 2014-08-07 Paper.tex
changed coxeter to lowercase c

In order to prove our main result, Theorem ~\ref{thm:main}, we must first define the Artin group associated to a finite type diagram. This definition will be similar to that made in \cite{BM13} at the beginning of Section 3, except that we shall not require $s_i^2 = e.$ Since Artin Groups are very similar to coxeter groups, with the caveat that the generators are not involutions, we will be able to use these modified relations to great effect.

>>>>

In order to prove our main result, Theorem ~\ref{thm:main}, we must first define the Artin group associated to a finite type diagram. This definition will be similar to that made in \cite{BM13} at the beginning of Section 3, except that we shall not require $s_i^2 = e.$ Since Artin Groups are very similar to Coxeter groups, with the caveat that the generators are not involutions, we will be able to use these modified relations to great effect.
